---
title: "MATH 216 Homework 4"
author: "Yuchen Zhu"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# Suggested packages; feel free to use more!
library(tidyverse)
library(USAboundaries)
library(maptools)
library(sp)
library(broom)
```



## Admistrative:

Please indicate

* Who you collaborated with:
* Roughly how much time you spent on this HW so far: 4
* The URL of the RPubs published URL [here](http://rpubs.com/ZhuYuchen/HW-4).
* What gave you the most trouble: coming up with a metrics to determine how good a place is as a shipping hub
* Any comments you have:



## Question 1:

**Question**:  DHL, a German shipping company, has a ton of money to build a
shipping hub in the United States. Where should they build it?

**Deliverable**: A choropleth map of the lower 48 states (no Puerto Rico) where
the color corresponds to the distance of the given area to the shipping hub,
which is marked on the map with a large red dot.

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# county-level map
counties_shp <- us_counties()
counties_data <- counties_shp@data
centroids <- coordinates(counties_shp)

counties_data <- cbind(counties_data, centroids)
colnames(counties_data)[11] <- "clongitude"
colnames(counties_data)[12] <- "clatitude"

counties_polygon <- tidy(counties_shp, region="geoid")

counties <- left_join(counties_polygon, counties_data, by=c("id"="geoid"))

counties <- counties %>%
  filter( !state_name %in% c("Alaska", "Hawaii", "Puerto Rico"))

map <- ggplot(counties, aes(x=long, y=lat, group=group)) +
        geom_path(size = 0.1) +
        coord_map()
map
```


```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# Perform your computations here:
# 1. How to select the hub's location (center of mass, population, infrastructure, tax, labor force, competition)

# - join population by county
PEP_2012_PEPANNRES_with_ann <- read_csv("~/Desktop/Fall 2016/MATH 216/HW-4/PEP_2012_PEPANNRES_with_ann.csv")

counties_pop <- PEP_2012_PEPANNRES_with_ann %>% 
  select(GEO.id2, rescen42010)
colnames(counties_pop)[1] <- "geoid"
colnames(counties_pop)[2] <- "population"

counties_data <- counties_data %>% 
  left_join(counties_pop, by="geoid") %>% 
  filter( !state_name %in% c("Alaska", "Hawaii", "Puerto Rico"))

# - find population center using center of mass (mass as population)
weighted_coord <- counties_data %>% 
  select(name, state_name, population, clongitude, clatitude) %>% 
  mutate(population = as.numeric(population)) %>% 
  mutate(clong_wgt = population*clongitude) %>% 
  mutate(clat_wgt = population*clatitude)

hub_x_coord <- sum(weighted_coord$clong_wgt)/sum(weighted_coord$population)
hub_y_coord <- sum(weighted_coord$clat_wgt)/sum(weighted_coord$population)

# - Population Center
c(hub_x_coord, hub_y_coord)

# 2. How to calculate distance (factor in direct distance, transportation convenience?)
counties_dist <- counties_data %>% 
  mutate(distance = sqrt((abs(clongitude)-abs(hub_x_coord))^2 
                         + (abs(clatitude)-abs(hub_y_coord))^2)
  ) %>% 
  select(geoid, population, distance)

counties <- left_join(counties, counties_dist, by=c("id" = "geoid"))

# 3. How to best graph: color, interactive, etc.
ggplot(data=counties, aes(x=long, y=lat, group=group, fill=distance)) +
  # Plot choropleth polygons, low -> high being colored white -> dark green
  geom_polygon() +
  scale_fill_gradient(low="white", high="darkgreen") + 
  # Trace outlines of areas
  geom_path(size=0.1) +
  # Mark hub
  annotate("point", x=hub_x_coord, y=hub_y_coord, col="red", size=5) +
  # Correct aspect ratio for map
  coord_map()
```

The population center I identified is -91.64791, 37.55090, which is the junciton of County Roads 647 and 608. It is within one-hour driving distance from Plato, MO, which is the official population center of the US accoridng to the 2010 census. The bias is reasonable since I used centroids of counties to calculate the population center of the US.

Since it is in the middle of nowhere, we also need to consider the population size & density, labor force size, and transportation infrastructure. An ideal shipping hub location should not only be close to the population center but also have sufficient infrastructure such as airport and empoyeable people.





